Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-10 papers/assembly/I/main.tex
Add some subsection headers
Set off pain points in red

\newcommand{\TODO}{\noindent\textbf{TODO:}~}

@@

@@

Before departing from the topic of the free commutative monoid, we want to note that while it may seem that we are being overly formalistic, we gain some power by taking this approach.
Most importantly, we can consider what happens if you ``map'' one set of objects into another. 
As a concrete example, you could imagine mapping each of the molecules $\ce{H_2}$, $\ce{O_2}$ and $\ce{H_2O}$ to the number of Hydrogen atoms they contain, i.e. $2$, $0$, and $2$.
\textbf{I don't like that example very much, but it's good enough for the moment.}
This mapping process can be ``lifted'' into a map on the linear combinations by distributing the map over addition, so that $\ce{H_2} + \ce{O_2}$ maps to $2 + 0 = 2$. More formally, any function between sets $f : X \rightarrow Y$ can be uniquely extended to a function $\N[f] : \N[X] \rightarrow \N[Y]$ such that
\begin{equation*}
    \sum_{x \in X} a_x x \mapsto \sum_{x \in X} a_x f(x).
\end{equation*}
The value of doing this is that it will allow us to coherently define a map between assembly spaces, to be defined, which will then be useful for proving certain theorems regarding bounds on quantities of interest.

@@

\begin{lemma}\label{lem:image-basis}
    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
    Then $f(\B)$ is a basis for $f(P)$.
\end{lemma}
\begin{proof}
    Certainly $f(\B)$ is nonempty as $\B$ is nonempty, and of course $f(P)$ must be in the upper set of $f(\B)$.
    This follows immediately from \cref{lem:image-of-pathways} since every site in $P$ is pathway connected to a site in $\B$.
    Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
    \TODO: Show that $f(\B)$ is minimal.
\end{proof}

@@

\begin{lemma}\label{lem:lower-is-rooted}
    Let $A$ be an assembly space and let $x \in S(A)$.
    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
\end{lemma}
\begin{proof}
    By construction, $\downset{x}$ is a Petri subnet of $A$.
    Since $A$ is an assembly space, it is sourceless and sinkless; and given that $\downset{x}$ is a site-completion, $\downset{x}$ is also sourceless and sinkless.
    This gives us that $\downset{x}$ is an assembly subspace of $A$.
    We need only show that $\B_{x\downarrow} = \B_A \cap S(\downset{x}) \subseteq \B_A$ is a basis of $\downset{x}$.
    First, $\B_{x\downarrow}$ is necessarily nonempty since $\B_A$ is a basis in $A$.
    Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
    \TODO: Show that $\B_{x\downarrow}$ is minimal.
\end{proof}

@@

\TODO Typeset split-branch algorithm

@@

\TODO Come up with a few fun examples.

>>>>

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\TODO}[1]{\noindent\red{\textbf{TODO:}~#1}}

@@

\subsection{Free Commutative Monoids}

@@

Before departing from the topic of the free commutative monoid, we want to note that while it may seem that we are being overly formalistic, we gain some power by taking this approach.
Most importantly, we can consider what happens if you ``map'' one set of objects into another. 
As a concrete example, you could imagine mapping each of the molecules $\ce{H_2}$, $\ce{O_2}$ and $\ce{H_2O}$ to the number of Hydrogen atoms they contain, i.e. $2$, $0$, and $2$.
\red{I don't like that example very much, but it's good enough for the moment.}
This mapping process can be ``lifted'' into a map on the linear combinations by distributing the map over addition, so that $\ce{H_2} + \ce{O_2}$ maps to $2 + 0 = 2$. More formally, any function between sets $f : X \rightarrow Y$ can be uniquely extended to a function $\N[f] : \N[X] \rightarrow \N[Y]$ such that
\begin{equation*}
    \sum_{x \in X} a_x x \mapsto \sum_{x \in X} a_x f(x).
\end{equation*}
The value of doing this is that it will allow us to coherently define a map between assembly spaces, to be defined, which will then be useful for proving certain theorems regarding bounds on quantities of interest.

\subsection{Petri Nets}

@@

\begin{lemma}\label{lem:image-basis}
    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
    Then $f(\B)$ is a basis for $f(P)$.
\end{lemma}
\begin{proof}
    Certainly $f(\B)$ is nonempty as $\B$ is nonempty, and of course $f(P)$ must be in the upper set of $f(\B)$.
    This follows immediately from \cref{lem:image-of-pathways} since every site in $P$ is pathway connected to a site in $\B$.
    Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
    \TODO{Show that $f(\B)$ is minimal.}
\end{proof}

@@

\begin{lemma}\label{lem:lower-is-rooted}
    Let $A$ be an assembly space and let $x \in S(A)$.
    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
\end{lemma}
\begin{proof}
    By construction, $\downset{x}$ is a Petri subnet of $A$.
    Since $A$ is an assembly space, it is sourceless and sinkless; and given that $\downset{x}$ is a site-completion, $\downset{x}$ is also sourceless and sinkless.
    This gives us that $\downset{x}$ is an assembly subspace of $A$.
    We need only show that $\B_{x\downarrow} = \B_A \cap S(\downset{x}) \subseteq \B_A$ is a basis of $\downset{x}$.
    First, $\B_{x\downarrow}$ is necessarily nonempty since $\B_A$ is a basis in $A$.
    Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
    \TODO{Show that $\B_{x\downarrow}$ is minimal.}
\end{proof}

@@

\TODO{Typeset split-branch algorithm}

@@

\TODO{Come up with a few fun examples.}
